\documentclass{resume} % Use the custom resume.cls style

\usepackage[sfdefault]{roboto}
\usepackage[T1]{fontenc}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Thomas O'Leary} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+44 7565 402 001} 
\address{\href{mailto:olearythomas01@gmail.com}{olearythomas01@gmail.com} \\ \href{https://thomasoleary.github.io/}{https://thomasoleary.github.io/}} %
% \\ \href{https://linkedin.com/in/linkedinURL}{MAKE LINKEDIN}

\begin{document}

%----------------------------------------------------------------------------------------
%   Personal Statement
%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Statement}
    I am a highly motivated, hardworking and determined individual who has recently graduated from Falmouth University. Although completing a degree oriented around games, I am interested in entering the tech industry and landing a role as a Software Developer.
\end{rSection}



%----------------------------------------------------------------------------------------
%   Education
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Computing For Games BSc (Hons)}, Falmouth University \hfill {September 2019 -- July 2022}\\
Grade: Second Class Honours Upper Division (2:1)
\\
{\bf BTEC Level 3 90 Credit - Extended Diploma - Creative C;omputing}, Uxbridge College \hfill{September 2017 -- July 2019}\\
Grade: Distinction*, Distinction, Distinction (D*DD)

\end{rSection}

%----------------------------------------------------------------------------------------
%   Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS} 
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Project Management and Version Control & Jira, Trello, Confluence, Agile, Git\\
%Version Control & Git \\
Game Engines & Unity, Unreal\\
Languages & C\#, Python, C++, OpenGL, LaTeX, R\\
Soft Skills & Time Management, Teamwork, Communication, Problem-Solving
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%   Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Castan - Gameplay Programmer} {(\href{https://store.steampowered.com/app/1836170/Castan/}{https://store.steampowered.com/app/1836170/Castan/})} \hfill \href{https://store.steampowered.com/app/1836170/Castan/}{Steam}
\begin{itemize}
    \itemsep -3pt {} 
        \item Multi-Disciplinary Team of 12 closely following the Agile methodology - consisting of artists, animators, designers and programmers.
        \item Primarily communicating between designers and animators to ensure implementations are satisfactory.
        \item Released in May on Steam for free.
\end{itemize}


\item \textbf{Dissertation - Final Year Project} {(\href{https://github.com/thomasoleary/dissertation}{https://github.com/thomasoleary/dissertation})} \hfill \href{https://github.com/thomasoleary/dissertation}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
        \item Researched into the comparison of procedural generation and human design with a focus on room interiors.
        \item Created a Multi-Agent system that generated a rooms' interior at run-time using the Unity Game Engine.
        \item Completed a Turing style A/B test with the help of 56 participants and analysed collected data for significance using the R programming language.
\end{itemize}


\item \textbf{OpenGL Terrain Generation - Personal Project} {(\href{https://github.com/thomasoleary/opengl-terrain}{https://github.com/thomasoleary/opengl-terrain})} \hfill \href{https://github.com/thomasoleary/opengl-terrainL}{GitHub}
\begin{itemize}
    \itemsep -3pt {}
        \item Created an application that procedurally generates a plane of vertices \& indices using C++ and OpenGL.
        \item Perlin noise was utilised to create the effect of natural looking terrain.
\end{itemize}

\end{rSection} 


%----------------------------------------------------------------------------------------
%   Experience
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

    \textbf{IT Consultant - Work Experience} \hfill June 2017 \& June 2019 \\
    TMD Technologies Ltd \hfill \textit{Hayes, London}
    \begin{itemize}
        \itemsep -3pt {} 
        \item Shadowed and observed the IT Departments day-to-day work also helped with resolving raised tickets by staff.
        \item Gained an understanding of how IT systems are maintained in a large business environment.
        \item Tasked with creating system-wide Outlook shortcuts for staff.
    \end{itemize}

    % \textbf{Shop Floor Assistant} \hfill August 2018 -- August 2019\\
    % The Entertainer \hfill \textit{Uxbridge, London}
    %     \begin{itemize}
        %     \itemsep -3pt {} 
        %         \item Communicate and Interact with customers as well as handling day-to-day transactiions.
        %         \item Work alongside colleagues to ensure the store is kept to a professional and representable standard.
        %         \item Picked by the Regional Manager to present my way of displaying a certain product as the sales from our store were significantly higher than others.  
        %     \end{itemize}
        
        
\end{rSection} 
    
% \begin{rSection}{Work Experience}
    % \vspace{-1.25em}
    % \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
    % \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
    % \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \end{rSection} 
        
%----------------------------------------------------------------------------------------
%   Hobbies
%----------------------------------------------------------------------------------------
\begin{rSection}{Hobbies} 
    \vspace{-1.25em}
    \item \textbf{Kayaking}
    \begin{itemize}
        \itemsep -3pt {} 
        \item Have a passion for many forms of kayaking and currently working towards achieving a Level 2 Qualification in coaching.
        \item Elected Vice President of the Falmouth Student Kayak Canoe Society at Falmouth University. Assisting in coaching and running weekly sessions for both beginner and experienced paddlers.
    \end{itemize}
    
    \item \textbf{Scout Association}
    \begin{itemize}
        \itemsep -3pt {} 
        \item Involved in Scouting since the age of 6 and have worked through all sections achieving some of the highest awards. Currently working towards achieving the highest award in Scouting - the Queen Scout Award whilst still volunteering as a leader at my local group.
    \end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%   References
%----------------------------------------------------------------------------------------
% \begin{rSection}{References}
%     References available upon request.
% \end{rSection}
        
        
        
\end{document}